Error Reporting Parsers: a Monad Transformer Approach

### 2013-07-20 article.tex
Make it build
Signed-off-by: Edward Z. Yang <ezyang@mit.edu>

For simplicity, only '\n' characters will count as newlines; every other character,
including tabs, will count as a single column on the same line.

@@

\Section{Parsec comparison}
A quick word about Parsec \cite{leijen}, a popular and battle-tested parser 
combinator library for Haskell:

>>>>

For simplicity, only '\\n' characters will count as newlines; every other character,
including tabs, will count as a single column on the same line.

@@

\section{Parsec comparison}
A quick word about Parsec \cite{leijen}, a popular and battle-tested parser 
combinator library for Haskell:
